A comparative analysis of penalized linear mixed models in structured genetic data

### 2021-02-16 main.tex
Adding '1000 replicates' and definition of TPR to relevant figure and table captions.

\begin{figure}[H]
    \centering
    \includegraphics[width = \textwidth]{figures/beta_mse.png}
    \caption{Estimation accuracy of different methods for different data types in the presence and absence of environmental confounding with 4 subpopulations.}
    \label{fig:mse}
\end{figure}

@@

\begin{table}[H]
\centering
\begin{tabularx}{400pt}{cclYYY}
\toprule
$\eta$ & $\xi$ & \multicolumn{1}{c}{Method} & 1D Linear Admixture & Independent Subpopulations & Empirical \\ 
\midrule
\multirow{6}{*}{0.5} & \multirow{3}{*}{0} & lasso & 0.25 (0.05) & 0.23 (0.05) & 0.37 (0.06) \\ 
& & PC-lasso & 0.23 (0.05) & 0.21 (0.05) & 0.36 (0.06) \\ 
& & LMM-lasso & 0.25 (0.05) & 0.23 (0.05) & 0.41 (0.06) \\ 
\cmidrule{2-6}
& \multirow{3}{*}{0.8} & lasso & 0.24 (0.05) & 0.26 (0.06) & 0.29 (0.06) \\ 
& & PC-lasso & 0.28 (0.05) & 0.36 (0.06) & 0.46 (0.06) \\ 
& &  LMM-lasso & 0.28 (0.05) & 0.39 (0.06) & 0.61 (0.06) \\ 
\bottomrule
\end{tabularx}
\caption{True positive rates, mean (SD), for different data types in the absence ($\xi = 0$) and presence ($\xi = 0.8$) of environmental effects. For the data sets with simulated genotypes, 4 subpopulations are present.}
\label{tab:var_sel}
\end{table}

@@

\begin{figure}[hbt]
\centering
\includegraphics[scale = 0.9]{figures/pop_inf_snps_box.png}
\caption{Absolute allele frequency differences of selected, non-causal SNPs across methods, in the presence and absence of environmental confounding for two Empirical subpopulations, $\eta = 0.5$.}
\label{fig:pop_inf}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale = 0.9]{figures/mse_diff_subpops.png}
    \caption{Relative performance of LMM-lasso, PC-lasso for fine and coarse subpopulation structures and varying levels of environmental confounding with Independent Subpopulations, $\eta = 0.5$. }
    \label{fig:big_vs_small}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width = \textwidth]{figures/eta_beta_hat.png}
     \caption{Estimation accuracy and computing time of LMM-lasso-Rakitsch and LMM-lasso-ggmix for $\bbeta$ and $\eta$ for varying $\eta$ levels and sample sizes with Independent Subpopulations data, coarse subpopulation structure, $\xi = 0.8$.}
    \label{fig:eta_beta_mse}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width = \textwidth]{figures/beta_mse.png}
    \caption{Estimation accuracy of different methods for different data types in the presence and absence of environmental confounding with 4 subpopulations. Mean and 1 SE bars displayed for 1000 replications.}
    \label{fig:mse}
\end{figure}

@@

\begin{table}[H]
\centering
\begin{tabularx}{400pt}{cclYYY}
\toprule
$\eta$ & $\xi$ & \multicolumn{1}{c}{Method} & 1D Linear Admixture & Independent Subpopulations & Empirical \\ 
\midrule
\multirow{6}{*}{0.5} & \multirow{3}{*}{0} & lasso & 0.25 (0.05) & 0.23 (0.05) & 0.37 (0.06) \\ 
& & PC-lasso & 0.23 (0.05) & 0.21 (0.05) & 0.36 (0.06) \\ 
& & LMM-lasso & 0.25 (0.05) & 0.23 (0.05) & 0.41 (0.06) \\ 
\cmidrule{2-6}
& \multirow{3}{*}{0.8} & lasso & 0.24 (0.05) & 0.26 (0.06) & 0.29 (0.06) \\ 
& & PC-lasso & 0.28 (0.05) & 0.36 (0.06) & 0.46 (0.06) \\ 
& &  LMM-lasso & 0.28 (0.05) & 0.39 (0.06) & 0.61 (0.06) \\ 
\bottomrule
\end{tabularx}
\caption{True positive rates, defined as the proportion of the 50 causal SNPs which are selected with the correct sign, for different data types in the absence ($\xi = 0$) and presence ($\xi = 0.8$) of environmental effects. For the data sets with simulated genotypes, 4 subpopulations are present. Mean (SD) of 1000 replications.}
\label{tab:var_sel}
\end{table}

@@

\begin{figure}[hbt]
\centering
\includegraphics[scale = 0.9]{figures/pop_inf_snps_box.png}
\caption{Absolute allele frequency differences of selected, non-causal SNPs across methods, in the presence and absence of environmental confounding for two Empirical subpopulations, $\eta = 0.5$, 1000 replications.}
\label{fig:pop_inf}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale = 0.9]{figures/mse_diff_subpops.png}
    \caption{Relative performance of LMM-lasso, PC-lasso for fine and coarse subpopulation structures and varying levels of environmental confounding with Independent Subpopulations, $\eta = 0.5$, 1000 replications.}
    \label{fig:big_vs_small}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width = \textwidth]{figures/eta_beta_hat.png}
     \caption{Estimation accuracy and computing time of LMM-lasso-Rakitsch and LMM-lasso-ggmix for $\bbeta$ and $\eta$ for varying $\eta$ levels and sample sizes with Independent Subpopulations data, coarse subpopulation structure, $\xi = 0.8$, 1000 replications.}
    \label{fig:eta_beta_mse}
\end{figure}
